Virtual Element Methods Without Extrinsic Stabilization

### 2023-09-27 ex_shared.tex
update

\author{Chunyu Chen\thanks{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China 
  (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}
\and Xuehai Huang\thanks{Corresponding author. School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
\and Huayi Wei\footnotemark[2]
}

>>>>

\author{Chunyu Chen\thanks{
    School of Mathematics and Computational Science, Xiangtan University; National
    Center of Applied Mathematics in Hunan, Hunan Key Laboratory for Computation
    and Simulation in Science and Engineering Xiangtan 411105, China
  (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}
\and Xuehai Huang\thanks{Corresponding author. School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
\and Huayi Wei\footnotemark[2]
}
